---
title: "vignette for RWildbook-demo-1 "
author: "Xinxin Huang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demo of pulling and searching data from Wildbook framework}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This demo shows you how to search and pull data from Wildbook framework with RWildbook package.
In this demo, all datasets below are searching for the same set of data which is all the encounter of individual "A-001" in "whaleshark.org".

The searchWB function provides the main interface to the Wilbook framework and can be used in
one of three ways.

* Case 1. You can supply filters based on the variables within the database.

```{r, eval=FALSE}
data1 <- searchWB(username="xinxin",
                  password="changeme",
                  baseURL ="whaleshark.org",
                  object="Encounter",
                  individualID=c("A-001"))
```

* Case 2. If you have the JDOQL query for the search, You can ignore the filter arguments.

```{r, eval=FALSE}
data2<- searchWB(username="xinxin",
                 password="changeme",
                 baseURL ="whaleshark.org",
                 jdoql="SELECT FROM org.ecocean.Encounter WHERE individualID == 'A-001'")
```

* Case 3.  If you have a searchURL on hand, you can directly open the URL with function "searchWB".

```{r, eval=FALSE}
data3 <- searchWB(searchURL = "http://xinxin:changeme@whaleshark.org/api/jdoql?SELECT FROM org.ecocean.Encounter WHERE individualID == 'A-001'")
```

