---
title: "vignette for RWildbook-demo-1 "
author: "Xinxin Huang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demo of pulling and searching data from Wildbook framework}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This demo shows you how to search and pull data from Wildbook framework with RWildbook package.
In this demo, all datasets below are searching for the same set of data which is all the encounter of individual "A-001" in "whaleshark.org".

The searchWB function provides the main interface to the Wilbook framework and can be used in
one of three ways.

* Case 1. If you have a search URL on hand. You can run the following code.

```{r, eval=FALSE}
data1 <- searchWB(searchURL = "http://xinxin:changeme@whaleshark.org/api/jdoql?SELECT FROM org.ecocean.Encounter WHERE individualID == 'A-001'")
```

* Case 2. If you do not have the search URL but have the JDOQL query for the search.

```{r, eval=FALSE}
data2<- searchWB(username="xinxin",
                 password="changeme",
                 baseURL ="whaleshark.org",
                 jdoql="SELECT FROM org.ecocean.Encounter WHERE individualID == 'A-001'")
```

* Case 3. If you do not have searchURL or the JDOQL query ready for searching the data.
You can supply filters based on the variables within the database.

```{r, eval=FALSE}
data3 <- searchWB(username="xinxin",
                  password="changeme",
                  baseURL ="whaleshark.org",
                  object="Encounter",
                  individualID=c("A-001"))
```
